{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

        \subsubsection{Discussion}
            We does not and cannot claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
            Our goal here is to show that this silly idea is absolutely ungrounded. 
            However, two things are clear. FR-WAPG performs better than V-FISTA and it doesn't require prior knowledge on parameter $L, \mu$.

>>>>

        \subsubsection{Discussion}
            We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
            Our goal here is to show that this silly idea is absolutely ungrounded. 
            However, two things are clear. FR-WAPG performs better than V-FISTA and it doesn't require prior knowledge on parameter $L, \mu$. 
            \par
            The results of R-WAPG is relevent because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
            Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
            Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
            \begin{align*}
                \alpha_{k + 1} 
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
                \right)
                \\
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2 + 2q - 4
                    }
                \right)
                \\
                &< 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2
                    }
                \right) \le 1. 
            \end{align*}
            Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
            Therefore, $\alpha_k \in (0, 1)$. 
            In the very unlikely case when $q = 1$
